### 2017-10-14 Gruba/06-perf.tex

The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary in Sub-Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
Mary has more followers than followees.
The Sina Microblog tag she made for herself is ``actress'' (演员).
As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
According to Sub-Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
Mary's short-term interest, e.g. from 09/01/2016 to 09/30/2016, is shown in Sub-Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵). So the results are in line with expectations, as drama (话剧) and stage (舞台) in Sub-Fig.\ \ref{fig:userFeatures:uf-7}.

\begin{figure*}
  \centering
  \subfigure{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
\end{figure*}

>>>>

The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary in Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
Mary has more followers than followees.
The Sina Microblog tag she made for herself is ``actress'' (演员).
As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
According to Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
Mary's short-term interest, e.g. from 09/01/2016 to 09/30/2016, is shown in Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵). So the results are in line with expectations, as drama (话剧) and stage (舞台) in Fig.\ \ref{fig:userFeatures:uf-7}.

\begin{figure*}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
\end{figure*}

### 2017-10-14 Gruba/10-appendix.tex

\newpage
\section{Appendix: Extra Experiments}
\label{sec:appendix}

%\subsection{Case Study for Feature Extraction}

\subsection{Case Study for User Clustering}

@@

\stab(1) Most users of group one are male (as shown in Sub-Fig. \ref{fig:subfig1:fig11}), and Sub-Fig. \ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京). The amount of their followees is mostly similar as their followers (as shown in Sub-Fig. \ref{fig:subfig1:fig14}). The most active time of this group is mainly between 10 am and 12 am (as shown in Sub-Fig. \ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).

\stab(2) Mostly users of group two are  female (as shown in Sub-Fig. \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Sub-Fig. \ref{fig:subfig2:fig22}). Similar to group one, most of them have followees close to followers (as shown in Sub-Fig. \ref{fig:subfig2:fig24}). The most active time of this group is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).

\stab(3) Most users of group three are male (as shown in Sub-Fig. \ref{fig:subfig3:fig31}). They come from a wide range of provinces (as shown in Sub-Fig. \ref{fig:subfig3:fig32}). Most of them have number of followers far more than followees (as shown in Sub-Fig. \ref{fig:subfig3:fig34}). The most active time of this group is mainly in 10-12 am and 10-12 pm (as shown in Sub-Fig. \ref{fig:subfig3:fig35} and \ref{fig:subfig3:fig36}).

\stab(4) Most users of group four are female (as shown in Sub-Fig. \ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Sub-Fig. \ref{fig:subfig4:fig42}). Most of these users have the amount  of followers far more than followees (as shown in Sub-Fig. \ref{fig:subfig4:fig44}). And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Sub-Fig. \ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).

According to Sub-Figs. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
the number distribution of microblogs for four groups is similar with each other.
We visualize each group's long-term interest expressed as words cloud (shown in Sub-Figs. \ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}). As we can see, group one and group three have similar interests.

\begin{figure*}
  \centering
  \subfigure{
  \label{fig:subfig1:fig11}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/11.eps}}
  \subfigure{
  \label{fig:subfig1:fig12}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/12.eps}}
  \subfigure{
  \label{fig:subfig1:fig13}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/13.eps}}
  \subfigure{
  \label{fig:subfig1:fig14}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/14.eps}}
  \subfigure{
  \label{fig:subfig1:fig15}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/15.eps}}
  \subfigure{
  \label{fig:subfig1:fig16}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/16.eps}}
  \subfigure{
  \label{fig:subfig1:fig17}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/17.eps}}
  \subfigure{
  \label{fig:subfig1:fig18}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/18.eps}}
  \subfigure{
  \label{fig:subfig1:fig19}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/19.eps}}
  \caption{The Statistics of User Group One}
  \label{fig:subfig1} %% label for entire figure
\end{figure*}

\begin{figure*}
  \centering
  \subfigure{
  \label{fig:subfig2:fig21}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/21.eps}}
  \subfigure{
  \label{fig:subfig2:fig22}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/22.eps}}
  \subfigure{
  \label{fig:subfig2:fig23}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/23.eps}}
  \subfigure{
  \label{fig:subfig2:fig24}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/24.eps}}
  \subfigure{
  \label{fig:subfig2:fig25}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/25.eps}}
  \subfigure{
  \label{fig:subfig2:fig26}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/26.eps}}
  \subfigure{
  \label{fig:subfig2:fig27}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/27.eps}}
  \subfigure{
  \label{fig:subfig2:fig28}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/28.eps}}
  \subfigure{
  \label{fig:subfig2:fig29}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/29.eps}}
  \caption{The Statistics of User Group Two}
  \label{fig:subfig2} %% label for entire figure
\end{figure*}

\begin{figure*}
  \centering
  \subfigure{
  \label{fig:subfig3:fig31}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/31.eps}}
  \subfigure{
  \label{fig:subfig3:fig32}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/32.eps}}
  \subfigure{
  \label{fig:subfig3:fig33}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/33.eps}}
  \subfigure{
  \label{fig:subfig3:fig34}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/34.eps}}
  \subfigure{
  \label{fig:subfig3:fig35}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/35.eps}}
  \subfigure{
  \label{fig:subfig3:fig36}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/36.eps}}
  \subfigure{
  \label{fig:subfig3:fig37}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/37.eps}}
  \subfigure{
  \label{fig:subfig3:fig38}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/38.eps}}
  \subfigure{
  \label{fig:subfig3:fig39}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/39.eps}}
  \caption{The Statistics of User Group Three}
  \label{fig:subfig3} %% label for entire figure
\end{figure*}

\begin{figure*}
  \centering
  \subfigure{
  \label{fig:subfig4:fig41}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/41.eps}}
  \subfigure{
  \label{fig:subfig4:fig42}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/42.eps}}
  \subfigure{
  \label{fig:subfig4:fig43}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/43.eps}}
  \subfigure{
  \label{fig:subfig4:fig44}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/44.eps}}
  \subfigure{
  \label{fig:subfig4:fig45}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/45.eps}}
  \subfigure{
  \label{fig:subfig4:fig46}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/46.eps}}
  \subfigure{
  \label{fig:subfig4:fig47}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/47.eps}}
  \subfigure{
  \label{fig:subfig4:fig48}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/48.eps}}
  \subfigure{
  \label{fig:subfig4:fig49}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/49.eps}}
  \caption{The Statistics of User Group Four}
  \label{fig:subfig4} %% label for entire figure
\end{figure*}

>>>>

\section*{Appendix: Extra Experiments}
\label{sec:appendix}

%\subsection{Case Study for Feature Extraction}
\begin{figure*}
  \centering
  \subfigure[]{
  \label{fig:subfig1:fig11}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/11.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig12}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/12.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig13}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/13.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig14}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/14.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig15}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/15.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig16}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/16.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig17}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/17.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig18}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/18.eps}}
  \subfigure[]{
  \label{fig:subfig1:fig19}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/19.eps}}
  \caption{The Statistics of User Group One}
  \label{fig:subfig1} %% label for entire figure
\end{figure*}

\subsection*{Exp-5: Case Study for User Clustering}

@@

\stab(1) Most users of group one are male (as shown in Fig. \ref{fig:subfig1:fig11}), and Fig. \ref{fig:subfig1:fig12} shows that they are mainly in Beijing(北京). The amount of their followees is mostly similar as their followers (as shown in Fig. \ref{fig:subfig1:fig14}). The most active time of this group is mainly between 10 am and 12 am (as shown in Fig. \ref{fig:subfig1:fig15} and \ref{fig:subfig1:fig16}).

\stab(2) Mostly users of group two are  female (as shown in Fig. \ref{fig:subfig2:fig21}) and are also mainly in Beijing (北京) (shown as Fig. \ref{fig:subfig2:fig22}). Similar to group one, most of them have followees close to followers (as shown in Fig. \ref{fig:subfig2:fig24}). The most active time of this group is mainly between 10 pm and 12 pm (as shown in Fig. \ref{fig:subfig2:fig25} and \ref{fig:subfig2:fig26}).

\stab(3) Most users of group three are male (as shown in Fig. \ref{fig:subfig3:fig31}). They come from a wide range of provinces (as shown in Fig. \ref{fig:subfig3:fig32}). Most of them have number of followers far more than followees (as shown in Fig. \ref{fig:subfig3:fig34}). The most active time of this group is mainly in 10-12 am and 10-12 pm (as shown in Fig. \ref{fig:subfig3:fig35} and \ref{fig:subfig3:fig36}).

\stab(4) Most users of group four are female (as shown in Fig. \ref{fig:subfig4:fig41}), and they come from a wide range of provinces just as group three (as shown in Fig. \ref{fig:subfig4:fig42}). Most of these users have the amount  of followers far more than followees (as shown in Fig. \ref{fig:subfig4:fig44}). And the most active time of these users is mainly between 10 pm and 12 pm (as shown in Fig. \ref{fig:subfig4:fig45} and \ref{fig:subfig4:fig46}).

According to Fig. \ref{fig:subfig1:fig13}, \ref{fig:subfig2:fig23}, \ref{fig:subfig3:fig33} and \ref{fig:subfig4:fig43},
the number distribution of microblogs for four groups is similar with each other.
We visualize each group's long-term interest expressed as words cloud (shown in Figs. \ref{fig:subfig1:fig19}, \ref{fig:subfig2:fig29}, \ref{fig:subfig3:fig39} and \ref{fig:subfig4:fig49}). As we can see, group one and group three have similar interests.

\begin{figure*}
  \centering
  \subfigure[]{
  \label{fig:subfig2:fig21}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/21.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig22}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/22.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig23}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/23.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig24}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/24.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig25}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/25.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig26}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/26.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig27}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/27.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig28}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/28.eps}}
  \subfigure[]{
  \label{fig:subfig2:fig29}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/29.eps}}
  \caption{The Statistics of User Group Two}
  \label{fig:subfig2} %% label for entire figure
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{
  \label{fig:subfig3:fig31}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/31.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig32}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/32.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig33}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/33.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig34}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/34.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig35}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/35.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig36}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/36.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig37}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/37.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig38}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/38.eps}}
  \subfigure[]{
  \label{fig:subfig3:fig39}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/39.eps}}
  \caption{The Statistics of User Group Three}
  \label{fig:subfig3} %% label for entire figure
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{
  \label{fig:subfig4:fig41}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/41.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig42}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/42.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig43}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/43.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig44}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/44.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig45}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/45.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig46}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/46.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig47}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/47.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig48}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/48.eps}}
  \subfigure[]{
  \label{fig:subfig4:fig49}
      \includegraphics[width=0.23\textwidth]{IMAGE/group-images/49.eps}}
  \caption{The Statistics of User Group Four}
  \label{fig:subfig4} %% label for entire figure
\end{figure*}
